---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cccmthemes

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![R-CMD-check](https://github.com/unhcr-dataviz/cccmthemes/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/unhcr-dataviz/cccmthemes/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/cccmthemes)](https://CRAN.R-project.org/package=cccmthemes)
<!-- badges: end -->

Simplify the creation of your data visualizations with the `{cccmthemes}` R package. It is designed to align your plots with [CCCM's Design Guide](https://www.cccmcluster.org/branding-collection) recommendations. This package offers a comprehensive `{ggplot2}` theme, including built-in customizations and thoughtfully crafted color palettes.

## Installation

Get started by installing the `{cccmthemes}` package from GitHub using the `{pak}` library:

```{r install, eval=FALSE}
# If pak is not yet installed, uncomment the following line:
# install.packages("pak")

pak::pkg_install("unhcr-dataviz/cccmthemes")
```

## Usage

```{r load, message = FALSE, warning = FALSE}
# Load required packages
library(ggplot2)
library(cccmthemes)
```

### Base `{ggplot2}` theme

```{r base-plot, message = FALSE, warning = FALSE, out.width="90%", fig.align="center"}
# Apply the theme_unhcr() to your plot
ggplot(
  mtcars,
  aes(x = hp, y = mpg)
) +
  geom_point() +
  labs(
    title = "Simple scatterplot with ggplot",
    subtitle = "This plot shows the default style of theme_cccm()",
    x = "Horsepower (hp)",
    y = "Fuel efficiency (mpg)",
    caption = "Source: mtcars"
  ) +
  theme_cccm()
```

### Font

The officially recommended font is [`Inter`](https://github.com/rsms/inter). To ensure optimal functionality of the `{cccmthemes}` package, please make sure that the `Inter` font is installed on your device prior to usage.

## Acknowledgements

We extend our gratitude to the creators of the [`{hrbrthemes}`](https://github.com/hrbrmstr/hrbrthemes), [`{cowplot}`](https://github.com/wilkelab/cowplot/) and [`{unhcrthemes}`](https://github.com/unhcr-dataviz/unhcrthemes) packages that influenced the development of `{cccmthemes}`.

## Contribution

Contributions to `{cccmthemes}` are highly valued. If you have suggestions, uncover bugs, or envision new features, kindly submit an [issue on GitHub](https://github.com/unhcr-dataviz/cccmthemes/issues). To contribute code, don't hesitate to fork the repository and create a pull request.

## License

This package is distributed under the [MIT License](https://github.com/unhcr-dataviz/cccmthemes/blob/master/LICENSE.md).